COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
Error fixen: Tabellen auskommentiert

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_physical_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_time_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_performance_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_effort_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_frustration_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis2a_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  h2c_ss.table
  , caption = "Simple slope analysis of SVs...XXX"
  , note = "XXX."
  , escape = FALSE
)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_mental_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_physical_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_time_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_performance_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_effort_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis1c_frustration_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
#apa_table(
#  hypothesis2a_contrasts
#  , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
#  , note = "XXX."
#  , escape = TRUE
#)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#apa_table(
#  h2c_ss.table
#  , caption = "Simple slope analysis of SVs...XXX"
#  , note = "XXX."
#  , escape = FALSE
#)
```
